\documentname: Is machine learning good or bad for the natural sciences?

### 2023-12-20 paper/main.tex
messing around

\clearpage\appendix
\section{\raggedright Population-level biases in regression outputs}
A machine-learning (ML) regression learns the best set of parameters or weights $\hat{\theta}$ of a flexible function $f(x;\theta)$ from a training set of labeled data.
The learned function $f(x;\hat{\theta})$ delivers a predicted or estimated label $\hat{y}$ for any data point with a complete set of features $x$.
Thus an estimated label $\hat{y}_\ast$ for a data point with features $x_\ast$ has taken information \emph{both} from the features $x_\ast$ and \emph{also} from the features and labels of all the data points in the training set used to set the weights $\hat{\theta}$.
In applications in which regression-estimated labels are used, it matters \emph{how much information} is coming from the individual data-point's features and how much from the original training set.

>>>>

\clearpage\appendix
\section{Population-level biases in regression outputs}
A machine-learning (ML) regression learns the best set of parameters or weights $\hat{\theta}$ of a flexible function $f(x;\theta)$ from a training set of labeled data.
The learned function $f(x;\hat{\theta})$ delivers a predicted or estimated label $\hat{y}$ for any data point with a complete set of features $x$.
Thus an estimated label $\hat{y}_\ast$ for a data point with features $x_\ast$ has taken information \emph{both} from the features $x_\ast$ and \emph{also} from the features and labels of all the data points in the training set used to set the weights $\hat{\theta}$.
In applications in which regression-estimated labels are used, it matters \emph{how much information} is coming from the individual data-point's features and how much from the original training set.
